### 2025-08-20 chapters/benchmark.tex
added random forest generation regression plot

To rigorously assess the significance of these observed performance trends, we applied both parametric and non-parametric statistical tests across all configurations. Specifically, a one-way ANOVA test was used to evaluate mean differences between scaling levels (under the assumption of normality), while the Kruskal–Wallis test assessed distributional differences in a non-parametric manner. These results are visualized in Figure~\ref{fig:combined-analysis}.

@@

% --- Subfigure (a): p-value Bar Chart ---
\begin{subfigure}[t]{0.9\linewidth}
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\linewidth,
    height=7cm,
    ybar,
    bar width=10pt,
    ymin=0, ymax=1,
    ymajorgrids,
    grid style=dashed,
    symbolic x coords={coremark, coremark.ke, dhrystone, dhrystone.ke, kyber, kyber.ke},
    xtick=data,
    xticklabel style={font=\small, rotate=30, anchor=east},
    enlarge x limits=0.15,
    ylabel={p-value},
    axis y line*=left,
    axis x line*=bottom,
    font=\small,
    legend style={font=\small, at={(0.5,1.1)}, anchor=south, legend columns=2},
    nodes near coords,
    every node near coord/.append style={
        font=\scriptsize,
        rotate=90,
        anchor=west,
        yshift=2pt
    }
]

@@

\end{axis}
\end{tikzpicture}
\caption{ANOVA and Kruskal-Wallis p-values for core and memory scaling. p-values below the $\alpha=0.05$ threshold (dashed line) indicate statistically significant effects.}
\label{fig:anova-kruskal}
\end{subfigure}

\vspace{1em}

% --- Subfigure (b): Regression Table ---
\begin{subfigure}[t]{0.9\linewidth}
\centering
\begin{threeparttable}
\caption{Linear regression coefficients of performance on hardware parameters.}
\label{tab:regression-coefs}
\begin{tabular}{@{}l
                S[table-format=7.3]
                S[table-format=7.3]
                S[table-format=7.3]
                S[table-format=7.3]@{}}
\toprule
\textbf{Workload} & \textbf{Intercept} & \textbf{Cores Coef.} & \textbf{Memory Coef.} & \textbf{$R^2$} \\
\midrule
\texttt{coremark}     & 102.805  & -0.508  & 0.008  & 0.038 \\
\texttt{coremark.ke}  & 122.474  & -2.970  & 0.007  & 0.071 \\
\texttt{dhrystone}    & 52.178   & -19.627 & 0.151  & 0.282 \\
\texttt{enclave.ke}   & 28.257   & 1.104   & -0.019 & 0.043 \\
\texttt{kyber}        & 89.318   & -40.129 & 0.329  & 0.035 \\
\texttt{kyber.ke}     & 42.219   & 0.824   & -0.029 & 0.070 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item Coefficients reflect linear regression fits across scaling increments.
\item Intercept approximates baseline performance; coefficients represent change per incremental unit of cores or memory.
\item \( R^2 \) indicates model fit (explained variance); values near zero imply weak correlation.
\end{tablenotes}
\end{threeparttable}
\caption*{}
\end{subfigure}

\caption{Statistical analysis of workload performance scaling. (a) ANOVA and Kruskal-Wallis tests evaluate whether core/memory scaling significantly affects performance. (b) Linear regression models estimate the effect magnitude and fit quality.}
\label{fig:combined-analysis}
\end{figure}

>>>>

To rigorously assess the significance of these observed performance trends, we applied both parametric and non-parametric statistical tests across all configurations. Specifically, a one-way ANOVA test was used to evaluate mean differences between scaling levels (under the assumption of normality), while the Kruskal–Wallis test assessed distributional differences in a non-parametric manner. These results are visualized in Figure~\ref{fig:combined-analysis-updated}.

%\footnote{The Kruskal-Wallis test was used alongside ANOVA to handle cases where group distributions violated normality assumptions, ensuring robustness in detecting group differences. Random Forest regression was applied in addition to linear models to address multicollinearity between hardware parameters (e.g., cores and memory), and to capture potential nonlinear relationships that linear regression may miss.}

@@

% --- Subfigure (a): p-value Bar Chart ---
\begin{subfigure}[t]{0.95\linewidth}
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\linewidth,
    height=7cm,
    ybar,
    bar width=10pt,
    ymin=0, ymax=1,
    ymajorgrids,
    grid style=dashed,
    symbolic x coords={coremark, coremark.ke, dhrystone, dhrystone.ke, kyber, kyber.ke},
    xtick=data,
    xticklabel style={font=\small, rotate=30, anchor=east},
    enlarge x limits=0.15,
    ylabel={p-value},
    axis y line*=left,
    axis x line*=bottom,
    font=\small,
    legend style={font=\small, at={(0.5,1.1)}, anchor=south, legend columns=2},
    nodes near coords,
    every node near coord/.append style={
        font=\scriptsize,
        rotate=90,
        anchor=west,
        yshift=2pt
    }
]

@@

\end{axis}
\end{tikzpicture}
\caption{ANOVA and Kruskal-Wallis p-values for core and memory scaling. p-values below the $\alpha=0.05$ threshold (dashed line) indicate statistically significant effects.}
\label{fig:anova-kruskal}
\vspace{0.5em}
{\footnotesize
\noindent\parbox{\linewidth}{%
\textit{Note: The Kruskal-Wallis test was included to address cases where normality assumptions were not met.}
}
}
\end{subfigure}

\vspace{1.5em}

% --- Subfigure (b): Grouped R^2 Chart ---
\begin{subfigure}[t]{0.95\linewidth}
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\linewidth,
    height=7cm,
    ybar,
    bar width=10pt,
    enlarge x limits=0.15,
    ylabel={$R^2$ (interaction model)},
    ymin=0, ymax=0.5,
    ymajorgrids,
    grid style=dashed,
    symbolic x coords={coremark,coremark.ke,dhrystone,dhrystone.ke,kyber,kyber.ke},
    xtick=data,
    xticklabel style={rotate=30,anchor=east, font=\small},
    font=\small,
    legend style={at={(0.5,1.1)}, anchor=south, legend columns=2},
    every node near coord/.append style={
        font=\footnotesize,
        rotate=90,
        anchor=west,
        /pgf/number format/fixed,
        /pgf/number format/precision=2
    },
    nodes near coords
]

% Linear regression
\addplot+[
    pattern=north east lines, 
    pattern color=black, 
    draw=black, 
    bar shift=-6pt
] coordinates {
    (coremark,0.04)
    (coremark.ke,0.07)
    (dhrystone,0.28)
    (dhrystone.ke,0.04)
    (kyber,0.33)
    (kyber.ke,0.24)
};

% Random Forest
\addplot+[
    pattern=horizontal lines, 
    pattern color=black, 
    draw=black, 
    bar shift=6pt
] coordinates {
    (coremark,0.07)
    (coremark.ke,0.40)
    (dhrystone,0.31)
    (dhrystone.ke,0.24)
    (kyber,0.36)
    (kyber.ke,0.23)
};

\legend{Linear regression, Random Forest}
\end{axis}
\end{tikzpicture}
\caption{Comparison of $R^2$ values from linear regression and random forest models across workloads. Higher values indicate better model fit.}
\label{fig:r2_grouped}
\vspace{0.5em}
{\footnotesize
\noindent\parbox{\linewidth}{%
\textit{Note: Random Forest regression was included to address multicollinearity issues observed in linear models.}
}
}
\end{subfigure}

\caption{Statistical analysis of workload performance scaling. (a) ANOVA and Kruskal-Wallis tests evaluate whether core/memory scaling significantly affects performance. (b) Regression models estimate the effect magnitude and fit quality.}
%\caption*{\textit{Note: A Random Forest regressor was used to mitigate multicollinearity effects between CPU cores and memory capacity, offering a non-linear alternative to standard linear regression.}}
\label{fig:combined-analysis-updated}
\end{figure}
